\Large \bf Traffic Sign Classification

### 2017-12-19 paper/main.tex
CNN paragraph

The techniques discussed here were selected from high performing approaches entered into the German Traffic Sign Recognition Benchmark (GTSRB) competition, or developed and tested on this dataset after the conclusion of the competition \cite{stallkamp_german_2011, stallkamp_man_2012}. This competition provides a high quality data set of traffic sign images split into training and test sets that can be used to design, validate, and compare approaches to traffic sign classification. The data set consists of 34799 training images and 12630 test images comprised of 43 classes. The data set is unbalanced, with class representation ranging from 0.5 \% and 5.5 \% of images \cite{stallkamp_german_2011}.

The German Traffic Sign Recognition Benchmark was originally formulated as a competition in two stages. Following the completion of the final stage, the GTSRB data set was made available online as a public benchmark to drive the development and empirical analysis of new classification algorithms \cite{stallkamp_german_2011, stallkamp_man_2012}. Here, I discuss the performance of classifiers entered at each stage of the competition, as well as other classifiers developed following the conclusion of the competition that provide an analysis based on the GTSRB data set.\footnote{It is worth noting that all of the published classifiers developed after 2012 that I have found as of this writing have provided an analysis using the GTSRB data set, so limiting discussion to approaches using this benchmark does not limit the scope of this paper.}

@@

While contrast and colour are fairly easy to define based on RBG and greyscale pixel values, other features are more difficult to represent. In particular, histograms of oriented gradient (HOG) are commonly used by image classification algorithms as a means of determining shape and orientation information. Briefly, the orientation of pixel values across image subregions are computed and combined hierarchically to produce feature vectors representing geometric information about an image \cite{stallkamp_german_2011, stallkamp_man_2012}. A number of other features were preprocessed and made available along with the GTSRB data set, but they were not used in any of the classifiers compared here, so they are not discussed.

@@

Linear discriminant analysis (LDA) ...
% TODO: What is LDA, how does it work, etc.

% TODO: How is LDA applied to traffic sign classification, how does it perform, etc.

@@

% TODO: SVMs

@@

Convolutional neural networks (CNNs) ...
% What are CNNs, how do they work, etc.

% How are CNNs applied to traffic sign classification, examine different implementations, etc.

@@

Linear discriminant analysis and support vector machines offer a significant performance advantage over neural networks, but at the cost of some accuracy. Although both LDA and SVM based techniques boast higher than 95 \% accuracy, this may not be acceptable for real-world sitations where recognizing and reacting to a sign is critical for passenger safety \cite{}. Moreover, the designers of the GTSRB competition note that some of the human control participants found the interface used to gather human responses was uninituitive and difficult to use \cite{stallkamp_german_2011, stallkamp_man_2012}. As a result, human performance may have been artificially low due to testing conditions, while the nature of the constructed data set was likely advantagous to the classifiers since each test case has a well defined class with none of the ambiguity associated with real-world driving scenarios. Thus, implementations that fail to match human performance in an artificial environment are likely not good candidates for use in real autonomous vehicles or other safety-critical applications.

@@

The model is made up of three pairs of feed-forward convolutional layers seperated by $2 \times 2$ max-pooling layers. Each of these pooling layers feeds into a dropout layer which drops $1/4^{th}$ of its inputs. The final set of convolutional, pooling, and dropout layers are flattened and passed into a classifier layer, which feeds into a softmax output layer that returns a probability distribution over the classes for a given input. The prediction for a given input is simply the maximum over this probability distribution.

@@

In order to assess the benefit of augmenting the data set with simple transformations of training images, I trained the model again on the same architecture, randomly applying a gaussian blur to half of the training examples. I observed a marginal improvement over the unaugmented data set, with the new model correctly classifying 96.00 \% of test images. Due to time limitations, it was not possible to experiment with other transformations, though I suspect that applying a random mix of transformations to generate the augmented data set would produce better results, since this technique has been used with considerable success in the past \cite{ciresan_committee_2011}. Figure 3 and Figure 4 show the accuracy and loss of the network over 200 training epochs when trained the augmented data set.

>>>>

The techniques discussed here were selected from high performing approaches entered into the German Traffic Sign Recognition Benchmark (GTSRB) competition, or developed and tested on this data set after the conclusion of the competition \cite{stallkamp_german_2011, stallkamp_man_2012}. This competition provides a high quality data set of traffic sign images split into training and test sets that can be used to design, validate, and compare approaches to traffic sign classification. The data set consists of 34799 training images and 12630 test images comprised of 43 classes. The data set is unbalanced, with class representation ranging from 0.5 \% and 5.5 \% of images \cite{stallkamp_german_2011}.

The German Traffic Sign Recognition Benchmark was originally formulated as a competition in two stages. Following the completion of the final stage, the GTSRB data set was made available online as a public benchmark to drive the development and empirical analysis of new classification algorithms. Additionally, human participants were also asked to classify images from the data set, correctly classifying 98.84 \% of examples on average \cite{stallkamp_german_2011, stallkamp_man_2012}. Here, I discuss the performance of classifiers entered at each stage of the competition, as well as other classifiers developed following the conclusion of the competition that provide an analysis based on the GTSRB data set.\footnote{It is worth noting that all of the published classifiers developed after 2012 that I have found as of this writing have provided an analysis using the GTSRB data set, so limiting discussion to approaches using this benchmark does not limit the scope of this paper.}

@@

While contrast and colour are fairly easy to define based on RBG and grey-scale pixel values, other features are more difficult to represent. In particular, histograms of oriented gradient (HOG) are commonly used by image classification algorithms as a means of determining shape and orientation information. Briefly, the orientation of pixel values across image subregions are computed and combined hierarchically to produce feature vectors representing geometric information about an image \cite{stallkamp_german_2011, stallkamp_man_2012}. A number of other features were preprocessed and made available along with the GTSRB data set, but they were not used in any of the classifiers compared here, so they are not discussed.

@@

Linear discriminant analysis (LDA) is a statistical method that can be used to find a linear combination of features characterizing a set of classes. Basic LDA can be used to construct a linear classifier separating two classes, but LDA classifiers can be combined to create higher dimensional classifiers, such as those needed for traffic sign recognition \cite{xanthopoulos2013linear}.

LDA gives fairly good results when applied to image classification problems, and is very fast both in training and classifying data \cite{hastie2001linear, mathias_traffic_2013}. LDA classifiers based on HOG features were used as a baseline model in the GTSRB competition, with the best implementation achieving a correct classification rate of 95.68 \%. While LDA is not as accurate as other methods, both training and classification time for the complete GTSRB data set are very low, on the order of seconds, making LDA very attractive for use with less powerful hardware in situations where real-time performance is required \cite{mathias_traffic_2013}.

@@

Support vector machines (SVMs) are binary linear classifiers designed to find the best separation between two classes based on a training data set. Like LDA implementations, SVMs can be used to produce non-linear and higher dimensional classifiers necessary for tasks such as traffic sign recognition \cite{mathias_traffic_2013}. SVM-based classifiers perform marginally worse on the GTSRB data set than LDA implementations, with the highest scoring solution correctly classifying 94.23 \% of examples in the training set \cite{mathias_traffic_2013}. Moreover, the time needed to train and test examples using SVMs is highly dependent on the features used, with high-performing implementations based on HOG features requiring upwards of 15 hours to train, though more efficient implementations require on the order of minutes to train and test on the complete GTSRB data set \cite{mathias_traffic_2013, stallkamp_german_2011}.

Overall, SVMs seem to exist in a ``worst of both worlds'' between neural networks and LDA implementations, exhibiting comparatively low correct classification rates at the expense of time intensive training and classification. This makes current SVM-based traffic sign classifiers poorly suited for real-world applications, though given that SVM performance is highly dependent on the feature set, it is possible that creating an efficient and performant SVM sign classifier is simply a matter of selecting the right feature set.

@@

Convolutional neural networks (CNNs) are multi-layer neural networks that consist of convolutional and pooling layers that feed forward into a classifier layer, which uses the inputs from previous stages to assign a probability distribution over a set of classes to a given example. CNNs are inspired by neurons in the visual cortex, where clusters of neurons process sensory data hierarchically, propagating signals in response to input patterns and allowing for fast, accurate recognition of visual stimuli. In CNNs, convolutional layers perform ``convolutions'' on inputs, such that each neuron in the layer responds to inputs for a specific region of input data, passing signals to layers further in the network. Pooling layers combine the output of clusters of neurons before sending an output to a neuron in the next layer. Finally, the output of the final stage is passed into a classifier, and a final output is ultimately used to assign a probability distribution to a given example \cite{ciresan_committee_2011, ciresan_multi-column_2012, sermanet_convolutional_2012, sermanet_traffic_2011}.

One of the major advantages of CNN-based approaches is that images require little preprocessing, and the classifier does not make use of handcrafted features during training or classification. Rather, features are inferred at each stage of the classifier by the network, which learns a classification function from the training set over a series of training ``epochs'', making architectures easy to generalize across related problems \cite{sermanet_convolutional_2012, sermanet_traffic_2011, stallkamp_german_2011, stallkamp_man_2012}.

Traffic sign classifiers based on CNNs perform well on the GTSRB data set, with the highest performing implementations reaching or exceeding human performance with the highest performing implementations  classifying between 98.31 \% and 99.17 \% of examples correctly. Unfortunately, the accuracy of CNNs comes at the cost of high training times, with training on the GTSRB data set taking on the order of hours and requiring access to powerful hardware \cite{sermanet_convolutional_2012, sermanet_traffic_2011, stallkamp_german_2011, stallkamp_man_2012}.

CNNs are capable of providing highly accurate classification at the cost of a relatively large initial time investment needed to train the model. Additionally, high performance CNNs often rely on costly hardware, making CNN implementations infeasible on low cost or lightweight embedded hardware.

@@

Linear discriminant analysis and support vector machines offer a significant performance advantage over neural networks, but at the cost of some accuracy. Although both LDA and SVM based techniques boast higher than 95 \% accuracy, this may not be acceptable for real-world situations where recognizing and reacting to a sign is critical for passenger safety \cite{}. Moreover, the designers of the GTSRB competition note that some of the human control participants found the interface used to gather human responses was uninituitive and difficult to use \cite{stallkamp_german_2011, stallkamp_man_2012}. As a result, human performance may have been artificially low due to testing conditions, while the nature of the constructed data set was likely advantageous to the classifiers since each test case has a well defined class with none of the ambiguity associated with real-world driving scenarios. Thus, implementations that fail to match human performance in an artificial environment are likely not good candidates for use in real autonomous vehicles or other safety-critical applications.

@@

The model is made up of three pairs of feed-forward convolutional layers separated by $2 \times 2$ max-pooling layers. Each of these pooling layers feeds into a dropout layer which drops $1/4^{th}$ of its inputs. The final set of convolutional, pooling, and dropout layers are flattened and passed into a classifier layer, which feeds into a softmax output layer that returns a probability distribution over the classes for a given input. The prediction for a given input is simply the maximum over this probability distribution.

@@

In order to assess the benefit of augmenting the data set with simple transformations of training images, I trained the model again on the same architecture, randomly applying a Gaussian blur to half of the training examples. I observed a marginal improvement over the unaugmented data set, with the new model correctly classifying 96.00 \% of test images. Due to time limitations, it was not possible to experiment with other transformations, though I suspect that applying a random mix of transformations to generate the augmented data set would produce better results, since this technique has been used with considerable success in the past \cite{ciresan_committee_2011}. Figure 3 and Figure 4 show the accuracy and loss of the network over 200 training epochs when trained the augmented data set.
